Check links on old pages

### 2024-06-28 src/audit-old-pages.qmd
Convert audit pages to Quarto

---
title: "Check links on old pages"
author: "Steve Simon"
date: "Created 2024-06-25"
output: html_document
---

@@

### create old

@@

### Search for links to old files

@@

### Search for size

@@

### Read file text

@@

@@

@@

### Simple statistics

>>>>

---
title: "Check links on old pages"
author: "Steve Simon"
date: "Created 2024-06-25"
execute:
  echo: false
format:
  html:
    embed-resources: true
---

@@

## Create old

@@

## Search for links to old files

@@

## Search for size

@@

## Read file text

@@

## Modify variables

@@

## Save results

@@

## Simple statistics
